On the Construction of a Collision-Free Schedule of Beacons in a Wireless Multi-Hop Network

### 2013-10-11 paper.tex
trying to fix vriable schedule size

These graph model represents strong assumptions because, in reality, wireless propagation is much more complicated.
The carrier sense range exceeds the transmission range and there is capture effect.
There are a large number of factors that determine whether a transmission is successful or not.
Nevertheless, for tractability, we use the above described graph model.

@@

Note that the starting and ending position of the schedule is only of local significance. 
We take the convention that each node considers the initial position of the schedule the one in which it transmits, and is numbered as zero.

@@

The challenge is to construct a schedule in such a way that all the neighbors of a station can listen to its beacon.
When such schedule is successfully constructed, all the nodes will receive confirmation of successful reception of its beacon from all neighboring stations.

@@

\subsection{The Interference Graph}
From the topology graph we derive the interference graph.
In the interference graph, there is an arc between two nodes the simultaneous transmission of those two nodes results in interference.
Given the interference graph, the problem finding the collision-free schedule of beacons reduces to a map coloring problem.

>>>>

This graph model represents strong assumptions because, in reality, wireless propagation is much more complicated.
The carrier sense range exceeds the transmission range and there is capture effect.
There are a large number of factors that determine whether a transmission is successful or not.
Nevertheless, for tractability, we use the above described graph model.

@@

Note that the starting and ending position of the schedule is only of local significance. 
We take the convention that each node considers the initial position of the schedule the one in which it has transmitted, and is numbered as zero.

@@

The challenge is to construct a schedule in such a way that all the stations can hear the beacons of all their neighbours.
When such schedule is successfully constructed, all the nodes will receive confirmation of successful reception of its beacon from all neighboring stations.

@@

\subsection{The Interference Graph}
From the topology graph we derive the interference graph.
In the interference graph, there is an arc between two nodes if the simultaneous transmission of those two nodes results in interference.
Given the interference graph, the problem finding the collision-free schedule of beacons reduces to a map coloring problem.
